Compare with SH HA paper

### 2017-01-20 Code/Run_model_on_SH_data/Prep SH HA data for our analysis.Rmd
small change

test.le.fx <- function(data, state, sex, race, year) {
  test.data <- data[data["State2"] == state & data["Sex2"] == sex & data["Race2"] == race & data["Year3"] == year, ]
  lt <- life.table(data = test.data, num.ages.in.group = "nx",
             death.counts = "Count", population.counts = "Population")
  return(round(lt$e_x[1], 1))
}

@@

test.le.fx(dtotal, "Alabama", "Male", "White", 1990)
test.le.fx(dtotal, "Alabama", "Male", "White", 2009)

test.le.fx(dtotal, "Alabama", "Male", "Black", 1990)
#test.le.fx(dtotal, "Alabama", "Male", "Black", 2009)

>>>>

test.le.fx <- function(data, state, sex, race, year) {
  test.data <- data[data["State2"] == state & 
                      data["Sex2"] == sex & 
                      data["Race2"] == race & 
                      data["Year3"] == year, ]

  lt <- life.table(data = test.data, num.ages.in.group = "nx",
                   death.counts = "Count", population.counts = "Population")
  return(round(lt$e_x[1], 1))
}

@@

test.le.fx(dtotal, "Alabama", "Male", "White", 2009)

test.le.fx(dtotal, "Alabama", "Male", "White", 1990)
test.le.fx(dtotal, "Alabama", "Male", "Black", 1990)
#test.le.fx(dtotal, "Alabama", "Male", "Black", 2009)
